Tables

### 2023-09-13 output/paper/figures.qmd
Working on structure of paper. Issues with cross-referencing tables in Quarto.

format:
  pdf:
    pdf-engine: lualatex
    toc: false
    include-in-header:
      text: |
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}

@@

execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
---

- Number figures according to the order in which they are first mentioned in the main text.
- Clearly label all axes, giving both the measure and the unit of measurement.
- Not larger than 7.5 inches in width.
- Save and submit each main text figure as an individual file (PDF with fonts embedded). Include the figure number in the file name of each figure.
- Provide main text figure captions on a new page of the main text after the tables.
- Include a title for the entire figure and descriptors for each panel.

# CTD Results
```{r}
#| label: fig-ctd-res
#| fig.cap: Barplot CTD.
#| fig.height: 10
#| fig.width: 10

path <- "results/files/CTD_chem_diseases_1680702221550_05042023.csv"
ctd <- myphd::load_ctd(path = path, 
                       filter_evidence = TRUE)
myphd::plot_ctd(ctd)
```

>>>>

format:
  pdf:
    pdf-engine: lualatex
    number-sections: true
    toc: false
    include-in-header:
      text: |
        \usepackage{lineno}
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}
    include-before-body:
      text: |
        \linenumbers

@@

editor_options: 
  chunk_output_type: console

execute:
  echo: false
  warning: false
  error: false
  message: false
---

- Number figures according to the order in which they are first mentioned in the main text.
- Clearly label all axes, giving both the measure and the unit of measurement.
- Not larger than 7.5 inches in width.
- Save and submit each main text figure as an individual file (PDF with fonts embedded). Include the figure number in the file name of each figure.
- Provide main text figure captions on a new page of the main text after the tables.
- Provide the title for each figure below the figure on the same manuscript page as the figure itself.
- Include a title for the entire figure and descriptors for each panel.

# Participants

- Flow diagram: number of individuals at each stage of study. Report numbers potentially eligible, examined for eligibility, confirmed eligible, included in the study, completing follow-up, and analysed.

# Main results

- Forest plot for RQ2 (group by chemical class, and for each chemical group bars for metabolites) and RQ3.

### 2023-09-13 output/paper/manuscript.qmd
Working on structure of paper. Issues with cross-referencing tables in Quarto.

---
metadata-files:
  - ../../../../all_phd/authors.yml

format:
  docx:
    reference-doc: reference_document.docx
  pdf:
    pdf-engine: lualatex
    number-sections: true
    toc: false
    include-in-header:
      text: |
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}
        \usepackage{lineno}

abstract: |
 **Background**

@@

filters:
  - ../../../../all_phd/_extensions/acronyms/parse-acronyms.lua
  - ../../../../all_phd/_extensions/authors-block/authors-block.lua
  - ../../../../all_phd/_extensions/wordcount/citeproc.lua
  - ../../../../all_phd/_extensions/wordcount/wordcount.lua

```{=latex}
\setcounter{tocdepth}{4}
\tableofcontents
```

---
title: "Some Fancy Title"
---

>>>>

---
title: "Some Fancy Title"

metadata-files:
  - ../../../../all_phd/authors.yml

format:
  docx:
    reference-doc: reference_document.docx
  pdf:
    pdf-engine: lualatex
    number-sections: true
    toc: false
    keep-tex: true
    include-in-header:
      text: |
        \usepackage{lineno}
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}
    include-before-body:
      text: |
        \linenumbers

filters:
  - authors-block
  - ../../../../all_phd/_extensions/acronyms/parse-acronyms.lua
  - ../../../../all_phd/_extensions/wordcount/citeproc.lua
  - ../../../../all_phd/_extensions/wordcount/wordcount.lua

# Abstract {.unnumbered}
**Background**

@@

### 2023-09-13 output/paper/si.qmd
Working on structure of paper. Issues with cross-referencing tables in Quarto.

execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
---

- Should be limited to results of secondary analyses and background details needed to ensure transparency:
  - Questionnaires.
  - Tables and figures with results of sensitivity analyses.
  - Tables with numeric data corresponding to results shown in the main text figures.
  - DAGs used to select model covariates.
- Text description of study methods should NOT go in the SM.
- Order the content: text, supplemental tables, and supplemental figures.
- Provide the title for each figure below the figure on the same manuscript page as the figure itself.
- Provide the title for each table above the table and the notes below the table.
- Number supplemental tables and figures separately according to the order in which they are first mentioned in the main text, using an "S" prefix.
- Conclude the SM with a list of references, even if they are also cited in the main paper.

>>>>

editor_options: 
  chunk_output_type: console

execute:
  echo: false
  warning: false
  error: false
  message: false
---

- Should be limited to results of secondary analyses and background details needed to ensure transparency:
  - Questionnaires.
  - Tables and figures with results of sensitivity analyses.
  - Tables with numeric data corresponding to results shown in the main text figures.
  - DAGs used to select model covariates.
- Text description of study methods should NOT go in the SM.
- Number supplemental tables and figures separately according to the order in which they are first mentioned in the main text, using an "S" prefix.

# Supplementary information

# Supplementary tables

- Provide the title for each table above the table and the notes below the table.

## Descriptive data

### Study populations

- Detailed characteristics of study participants (demographic, clinical, social), by cohort and overall.

# Supplementary figures

- Provide the title for each figure below the figure on the same manuscript page as the figure itself.

## Main results

- ADRF and AMEF for RQ2 and RQ3.
- Whole distribution (i.e., density) of e.g., risk differences (instead of marginalized estimates), with lines for mean and median.

# References {.unnumbered}

::: {#refs}
:::

### 2023-09-13 output/paper/tables.qmd
Working on structure of paper. Issues with cross-referencing tables in Quarto.

link-citations: true
linkcolor: blue

execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
---

- Begin each table on a new page after the list of references.
- Tables may not contain parts.
- List footnotes after the general one, one per line and indicated with a lowercase italicized letter.

# Study populations
```{r}

```

# Exposures
```{r}
#| label: tbl-chem-info
#| tbl-cap: Information about the non-persistent EDCs.

edcs_info <- myphd::edcs_information() |>
  tidylog::select(-c(chem_id, smiles))
gt::gt(edcs_info, groupname_col = "class") |>
  gt::cols_label(
    full_name = "Compound", 
    short_name = "Symbol", 
    pubchem_cid = "PubChem CID", 
    ctd_id = "CTD ID", 
    exposome_explorer_id = "Exposome Explore ID", 
    parental_compound = "Parental compound"
  ) |>
  gt::tab_style(
    locations = gt::cells_column_labels(columns = everything()), 
    style = list(
      gt::cell_borders(sides = "bottom", weight = gt::px(3)), 
      gt::cell_text(weight = "bold")
    )
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()), 
    style = list(gt::cell_text(weight = "bold"))
  )
```

>>>>

tbl-cap-location: top
link-citations: true
linkcolor: blue

editor_options: 
  chunk_output_type: console

execute:
  echo: false
  warning: false
  error: false
  message: false
---

- Begin each table on a new page after the list of references.
- Tables may not contain parts.
- Provide the title for each table above the table and the notes below the table.
- List footnotes after the general one, one per line and indicated with a lowercase italicized letter.

# Descriptive data

## Study populations

- Basic characteristics of study participants (demographic, clinical, social), by cohort and overall.
  - Include all covariates included in primary or secondary analyses.
  - Indicate number of participants with missing data for each variable of interest.
  - Report numbers of outcome events or summary measures.

## Endocrine disruptors

- Levels of unprocessed biomarkers (chemicals), with IDs.
- Report: minimum and maximum, percentiles, and number of observations above/below the assay's LOD and LOQ.

```{r}
#| label: tbl-chem-info
#| tbl-cap: "Information about the non-persistent EDCs."

edcs_info <- myphd::edcs_information() |>
  tidylog::select(-c(chem_id, smiles))
gt::gt(edcs_info,
       groupname_col = "class") |>
  gt::tab_header(
    title = "Information about the non-persistent EDCs."
  ) |>
  gt::cols_label(
    full_name = "Compound",
    short_name = "Symbol",
    pubchem_cid = "PubChem CID",
    ctd_id = "CTD ID",
    exposome_explorer_id = "Exposome Explore ID",
    parental_compound = "Parental compound"
  ) |>
  gt::tab_style(
    locations = gt::cells_column_labels(columns = everything()),
    style = list(
      gt::cell_borders(sides = "bottom", weight = gt::px(3)),
      gt::cell_text(weight = "bold")
    )
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```

## Corticosteroids

- Levels of unprocessed biomarkers (metabolites), with IDs.

# Main results

- RQ2: group chemicals by class, and for each chemical report results with metabolites (`avg_comparisons` with estimate, SE, s-value, CI).
- RQ3: report results with outcome (`avg_comparisons` with estimate, SE, s-value, CI).

# Other analyses
